Eurovision Song Contest: semifinal 1, 2009

### 2021-05-06 inst/eurovision.Rmd
consistency check

>>>>

Observe the small estimated strength for Czechoslovakia (`CZ`) at
about `1e-06`.  This is consistent with the second row of `preference`
which shows that noone gave them any points.

```{r,consistencycheck,cache=TRUE,fig.cap="consistency check: maximum likelihood obtained two different ways.  Exact agreement corresponds to points lying on the diagonal line.  Note the small estimated strength of Czechoslovakia"}
consistency(eurovision)
```
